---

title: "Data Analysis using R"
author: "Group 10"
date: "`r Sys.Date()`"
output: pdf_document

---



```{r setup, include=FALSE}
# Load required libraries
library(dplyr)
library(ggplot2)
library(tidyr)
```

## **1. Load the Dataset**
```{r}
# Import dataset
df <- read.csv("D:/c.csv", stringsAsFactors = FALSE)

# Print dataset structure
str(df)
```

## **2. List Variables in the Dataset**
```{r}
colnames(df)
```

## **3. Display the First 15 Rows**
```{r}
head(df, 15)
```

## **4. Create a User-Defined Function**
```{r}
total_sales <- function(x) {
  total_sales_made <- sum(x, na.rm = TRUE)
  return(total_sales_made)
}

df$Amount_clean <- gsub("[\\$,]", "", df$Amount, perl = TRUE)
df$Amount_numeric <- as.numeric(df$Amount_clean)
y <- total_sales(df$Amount_numeric)
print(y)
```

## **5. Remove Missing Values**
```{r}
df <- df %>% drop_na()
print("Data after removing missing values:")
head(df, 10)
```

## **6. Remove Duplicates**
```{r}
df <- df %>% distinct()
print("Data after removing duplicates:")
head(df, 10)
```

## **7. Filter Data (Amount > 5000)**
```{r}
df_filtered <- df %>% filter(Amount_numeric > 5000)
print("Filtered data (Amount > 5000):")
head(df_filtered, 10)
```

## **8. Sort Data by Amount (Descending Order)**
```{r}
df <- df %>% arrange(desc(Amount_numeric))
print("Sorted Data:")
head(df, 10)
```

## **9. Rename Columns**
```{r}
df <- df %>% rename(Salesperson = Sales.Person, Shipment_Count = Boxes.Shipped)
print("Renamed Columns:")
head(df, 10)
```

## **10. Add a New Column**
```{r}
df <- df %>% mutate(Double_Amount = Amount_numeric * 2)
print("New Column Added:")
head(df, 10)
```

## **11. Create a Training Set**
```{r}
set.seed(123)
train_index <- sample(1:nrow(df), 0.7 * nrow(df))
train_set <- df[train_index, ]
test_set <- df[-train_index, ]

print("Training Set (First 10 rows):")
head(train_set, 10)

print("Test Set (First 10 rows):")
head(test_set, 10)
```

## **12. Summary Statistics**
```{r}
summary(df)
```

## **13. Statistical Calculations**
```{r}
mean_value <- mean(df$Amount_numeric, na.rm = TRUE)
median_value <- median(df$Amount_numeric, na.rm = TRUE)

mode_func <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
mode_value <- mode_func(df$Amount_numeric)
range_value <- range(df$Amount_numeric, na.rm = TRUE)

print(mean_value)
print(median_value)
print(mode_value)
print(range_value)
```

## **14. Scatter Plot**
```{r}
ggplot(df, aes(x = Shipment_Count, y = Amount_numeric)) +
  geom_point() +
  ggtitle("Scatter Plot of Shipment Count vs. Amount")
```

## **15. Bar Plot**
```{r}
ggplot(df, aes(x = Salesperson, y = Amount_numeric, fill = Salesperson)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle("Bar Plot of Salesperson vs. Amount")
```

## **16. Correlation Calculation**
```{r}
correlation <- cor(df$Amount_numeric, df$Shipment_Count, use = "complete.obs", method = "pearson")
print(correlation)